Highly Available Transactions: Virtues and Limitations

### 2013-03-26 writeup/intro.tex
blooml and stuff

While this model classification is useful, we also seek to understand
the implications for end-users of HAT systems. HATs provide high
availability and low latency but cannot offer all of the semantic
guarantees of unavailable systems---when is this trade-off worthwhile?
We attempt to objectively study these virtues and limitations of both
classic and HAT systems by performing an extensive survey of
practitioner accounts and research literature, performing experimental
analyses on modern cloud infrastructure, and analyzing representative
applications for their semantic requirements. While our results are
not definitive for all applications, they suggest that HATs offer a
one to three order of magnitude latency decrease compared to
traditional protocols and provide acceptable semantics for a wide
range of programs, particularly those with monotonic logic and
commutative updates. HAT systems can also provide arbitrary foreign
key constraints on multi-item updates and sometimes provide uniqeness
guarantees. However, particularly for programs with non-monotonic
logic, HATs may fall short, requiring more coordination-intensive
mechanisms. Concisely, we attempt to understand \textit{what benefits
  do Highly Available Transactions offer and what is their cost?}

>>>>

While this model classification is useful, we also seek to understand
the implications for end-users of HAT systems. HATs provide high
availability and low latency but cannot offer all of the semantic
guarantees of unavailable systems---when is this trade-off worthwhile?
We attempt to objectively study these virtues and limitations of both
classic and HAT systems by performing an extensive survey of
practitioner accounts and research literature, performing experimental
analyses on modern cloud infrastructure, and analyzing representative
applications for their semantic requirements. While our results are
not definitive for all applications, they suggest that HATs offer a
one to three order of magnitude latency decrease compared to
traditional protocols and provide acceptable semantics for a wide
range of programs, particularly those with monotonic logic and
commutative updates~\cite{calm, blooml, crdt}. HAT systems can also provide
arbitrary foreign key constraints on multi-item updates and sometimes
provide uniqeness guarantees. However, particularly for programs with
non-monotonic logic, HATs may fall short, requiring more
coordination-intensive mechanisms. Concisely, we attempt to understand
\textit{what benefits do Highly Available Transactions offer and what
  is their cost?}
